Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-03 analysis/paper/paper.Rmd
remove redundant 'availability'

When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B; Table S2).

>>>>

When predicting the availability of data as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B; Table S2).
